---
title: "MCMC diagnostics"
output: 
  html_document:
    toc: true
    toc_float: true
    depth: 2
params:
  run: "1000"
  modelDir: !r here::here("model/pk")
  script: "template-mcmc.Rmd"
  n_per_page: 4
  myTheme: !r theme(text = element_text(size = 12), axis.text = element_text(size = 10))
  include_code: FALSE
  include_plots: TRUE
# n_thin: select every `n_thin` samples for trace/density plots
  n_thin: 1
# n_thin2: select every `n_thin2` samples for Bayes pairs plots
  n_thin2: 10
# theta_cov: indices of covariate THETAs to separate when creating pairs plots, e.g. !r c(1, 2, 6)
#   set to NULL to create a single pairs plot for THETAs
  theta_cov: NULL
#  theta_cov: !r c(6, 7, 8)
  run_mrggsave: TRUE
---

# Run number `r params$run`

To produce a set of MCMC diagnostic plots that will be included in a report. Please
note that these plots are just meant to provide an example of what could be
created and how. They are not an exhaustive list of every possible plot and were
chosen with the project aims in mind.

# Set up

```{r setup_general, include = F}
### General script set-up
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.height = 5,
  fig.width = 5
)

### Libraries ----------------------------
suppressPackageStartupMessages(library(tidyverse))
library(pmplots)
library(bbr)
library(bbr.bayes)
suppressPackageStartupMessages(library(posterior))
library(bayesplot)
library(mrggsave)
library(pmtables)
library(mrgsolve)
library(patchwork)
library(loo)
library(glue)
library(cowplot)
library(here)

### Directories ----------------------------
figDir <- here::here("deliv", "figure", "report")
dataDir <- here::here("data")

if (!file.exists(figDir)) dir.create(figDir)

thisScript <- params$script
options(
  mrg.script = params$script,
  mrggsave.dev = "pdf,png"
)

this_theme <- pmplots::pm_theme() + params$myTheme
theme_set(this_theme)
n_per_page <- params$n_per_page
```


```{r load_any_functions, include = F}
### Source function scripts
source(here::here("script/functions-diagnostics-rhat-ess.R"))
source(here::here("script/functions-mcmc-diagnostics.R"))
```

### Model location

Define `modelName` and path to the model directory (`MODEL_DIR`).

```{r setup_bbr, echo = params$include_code, message = FALSE}
# Set directories for bbr models ----------------------------
MODEL_DIR <- params$modelDir
modelName <- params$run
thisModelPath <- file.path(MODEL_DIR, modelName)
```

### Figure location

If saving figures out to pdf, define where those pdfs should be saved to.
Here the figures are saved to ```deliv > figure > model_run_number```

```{r makeDir_mrggsave, echo = params$include_code, eval = params$run_mrggsave}
thisFigDir <- file.path(figDir, modelName)
if (!file.exists(thisFigDir)) dir.create(thisFigDir)

### set mrggsave figure directory here
options(mrggsave.dir = thisFigDir)
```



# Model details

A summary of high-level model details.

Read in the model details using `read_model`. Details stored in the `mod` object
can be used to identify the location of the source data (used in $DATA) - to see
how this is done look at the `bbr::get_data_path()` and
`bbr::build_path_from_model()` helper functions.

```{r modelDetails, echo = params$include_code, results = "asis"}
mod <- read_model(file.path(MODEL_DIR, params$run))
mod
```

### Read output

```{r modelOutputSummary, echo = params$include_code}
# `draws_array` object from the `posterior` package
draws <- read_fit_model(mod)
n_chains <- nchains(draws)
n_iter <- niterations(draws)
pars <- dimnames(draws)$variable

# Summary of the posterior 
draws_param <- subset_draws(draws, variable = c("THETA", "OMEGA", "SIGMA"))
draws_sum <- draws_param %>% 
  summarize_draws()

fixed <- is.na(draws_sum$rhat)
pars_to_plot <- variables(draws_param)[!fixed]
iter_to_plot <- seq_len(n_iter)[seq_len(n_iter) %% params$n_thin == 0]
draws_param_plot <- subset_draws(draws_param, variable = pars_to_plot)
draws_param_thin <- subset_draws(draws_param_plot, iteration = iter_to_plot)
iter_to_plot2 <- seq_len(n_iter)[seq_len(n_iter) %% params$n_thin2 == 0]
draws_param_thin2 <- subset_draws(draws_param_plot, iteration = iter_to_plot2)
```

## Parameter estimates 

Compute summaries of posterior distributions as well as some diagnostics.

Bulk effective sample size (ESS) is a measure of sampling efficiency for the
location of the distribution, while Tail ESS is a measure of sampling efficiency
for the tails (5% and 95% quantiles) of the distribution. Higher values indicate
greater sampling efficiency.  A very rough rule of thumb is to aim for at least
400 for each parameter.

R-hat is a convergence diagnostic that compares the between- and within-chain
variances of model parameters. Values close to 1 indicate that the chains have
converged to similar distributions.  Aim for less than about 1.05 for all
parameters.

```{r summary, echo = FALSE}
ptable <- draws_sum %>% 
  mutate_if(is.numeric, ~formatC(., 3)) %>% 
  rename(parameter = variable) %>%
  mutate("90% CI" = paste("(", q5, ", ", q95, ")", 
                          sep = "")) %>%
  select(parameter, mean, median, sd, mad, "90% CI", ess_bulk, ess_tail, rhat)

ptable %>% 
  knitr::kable(caption = "Summary of model parameter estimates.")
```


# MCMC diagnostic plots

These plots assess whether all of the chains have converged to a single,
stationary distribution.

## Rhat

```{r rhat, echo = params$include_code}
rhats <- draws_sum$rhat
names(rhats) <- draws_sum$variable
rhat_plot <- mcmc_rhat(rhats) + yaxis_text()
```

```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
rhat_plot
```

```{r save_rhat_plot, include = FALSE, eval = params$run_mrggsave, message = FALSE}
# save plots to disk
mrggsave(
  rhat_plot, 
  script = params$script,
  stem = "{modelName}-rhat"
)
```

## Pairs

Look for any strong correlation between parameters, indicating possible
over-parameterisation.

```{r param_pairs_plots, echo = params$include_code, message=FALSE}
names_theta <- variables(draws_param_thin2) %>% str_subset("^THETA")
if (is.null(params$theta_cov)) {
  names_fixed_noncov <- names_theta
} else {
  names_fixed_cov <- intersect(
    names_theta,
    paste0("THETA[", params$theta_cov, "]")
  )
  names_fixed_noncov <- setdiff(names_theta, names_fixed_cov)
}

names_random <- variables(draws_param_thin2) %>%
  str_subset("^OMEGA|^SIGMA") %>% 
  # remove off-diagonals for pairs plots
  str_subset("\\[(\\d+),\\1\\]")

p_fixed_noncov <- mcmc_pairs(draws_param_thin2, pars = names_fixed_noncov)
p_random <- mcmc_pairs(draws_param_thin2, pars = names_random)
if (!is.null(params$theta_cov)) {
  p_fixed_cov <- mcmc_pairs(draws_param_thin2, pars = names_theta_cov)
}
```

```{r include_param_pairs, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE, fig.width=9, fig.height=9}
p_fixed_noncov
if (!is.null(params$theta_cov)) p_fixed_cov
p_random
```

```{r save_param_pairs, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p_fixed_noncov,
  stem = c(params$run, "pairs-fixed-noncov"),
  width = 9,
  height = 9
)
if (!is.null(params$theta_cov)) {
  mrggsave(
    p_fixed_cov,
    stem = c(params$run, "pairs-fixed-cov"),
    width = 9,
    height = 9
  )
}
mrggsave(
  p_random,
  stem = c(params$run, "pairs-random"),
  width = 9,
  height = 9
)
```

```{r rm_param_pairs, include=F}
rm(p_fixed_noncov, p_random)
if (!is.null(params$theta_cov)) rm(p_fixed_cov)
```

## ESS

```{r ess_bulk, echo = params$include_code}
ess_bulk <- draws_sum$ess_bulk
names(ess_bulk) <- draws_sum$variable
ess_bulk_ratios <- ess_bulk / (n_iter * n_chains)
ess_bulk_plot <- mcmc_neff(ess_bulk_ratios) + yaxis_text() +
  labs(title = "Bulk ESS ratios")
```
```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
ess_bulk_plot
```

```{r ess_tail, echo = params$include_code}
ess_tail <- draws_sum$ess_tail
names(ess_tail) <- draws_sum$variable
ess_tail_ratios <- ess_tail / (n_iter * n_chains)
ess_tail_plot <- mcmc_neff(ess_tail_ratios) + yaxis_text() +
  labs(title = "Tail ESS ratios")
```
```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
ess_tail_plot
```

```{r save_ess_plots, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  ess_bulk_plot, 
  stem = "{modelName}-ess-bulk"
)
mrggsave(
  ess_tail_plot, 
  stem = "{modelName}-ess-tail"
)
```

## ESS vs sample

Plots Bulk and Tail ESS versus iteration to check that ESS increases linearly.

```{r ess_vs_sample_plots, echo = params$include_code, message=FALSE}
# param_array <- as_draws_array(draws_param)
p <- map(variables(draws_param_plot), function(.x) {
  plot_change_ess(draws_param, .x)
}) %>%
  purrr::compact() # remove NULL elements of list

pESSsample <- p
```

```{r include_ess_vs_sample_plots, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_ess_vs_sample_plots, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  stem = c(params$run, "ess-vs-sample"),
  width = 5,
  height = 5
)
```

```{r rm_ess_vs_sample, include=F}
rm(p)
```

## ESS vs quantile

Plots Bulk and Tail ESS versus quantile to better diagnose areas of the
distributions that the iterative algorithm fails to explore efficiently.

```{r ess_vs_quantile_plots, echo = params$include_code, message=FALSE}
p <- map(variables(draws_param_plot), function(.x) {
  plot_quantile_ess(draws_param_plot, .x)
}) # %>%
# purrr::compact() # remove NULL elements of list

pESSquantile <- p
```

```{r include_ess_vs_quantile_plots, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_ess_vs_quantile_plots, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  stem = c(params$run, "ess-vs-quantile"),
  width = 5,
  height = 5
)
```

```{r rm_ess_vs_quantile, include=F}
rm(p)
```



## History plots

```{r history, echo = params$include_code}
mcmc_history_plots <- mcmc_history(
  draws_param_thin,
  pars = pars, 
  nParPerPage = n_per_page,
  myTheme = this_theme,
  np = NULL
)
```                                   
```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
mcmc_history_plots
```

```{r save_history_plots, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  mcmc_history_plots, 
  stem = "{modelName}-mcmc-history", 
  width = 5,
  height = 7
)
```

## Rank plots

```{r rank, echo = params$include_code}
mcmc_rank_plots <- mcmc_rank(
  draws_param_plot,
  pars = pars, 
  nParPerPage = n_per_page,
  myTheme = this_theme
)
```                                   
```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
mcmc_rank_plots
```
```{r save_rank_plots, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  mcmc_rank_plots, 
  stem = "{modelName}-mcmc-rank", 
  width = 5,
  height = 7
)
```

## Density plots

```{r density, echo = params$include_code}
mcmc_density_chain_plots <- mcmc_density(
  draws_param_plot,
  pars = pars, 
  nParPerPage = n_per_page,
  byChain = TRUE, 
  myTheme = this_theme)
```
```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
mcmc_density_chain_plots
```

```{r density2, echo = params$include_code}
mcmc_density_plots <- mcmc_density(
  draws_param_plot,
  pars = pars, 
  nParPerPage = n_per_page, 
  myTheme = this_theme
)
```
```{r eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
# show plot in HTML output
mcmc_density_plots
```

```{r save_density_plots, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  mcmc_density_chain_plots, 
  stem = "{modelName}-density-chain", 
  width = 5,
  height = 7
)
mrggsave(
  mcmc_density_plots, 
  stem = "{modelName}-density", 
  width = 5,
  height = 7
)
```

# Session details

It is considered good practice to include these details at the end of all rmd scripts

```{r details, include = TRUE}
Sys.getenv("AMI_NAME")
sessioninfo::session_info()
bbr::bbi_version()
```
