---
title: "Model diagnostics"
output: 
  html_document:
    toc: true
    toc_float: true
    depth: 2
params:
  run: "1000"
  logDV: FALSE
  modelDir: !r here::here("model/pk")
  script: "template-model-bayes.Rmd"
  yspec: !r here::here("data/derived/pk.yml")
  contCov: !r c("AGE","WT","ALB","EGFR")
  catCov: !r c("STUDY", "RF", "CP", "DOSE")
  etas: !r c("ETA1//ETA-KA", "ETA2//ETA-V/F", "ETA3//ETA-CL/F")
  include_code: FALSE
  include_plots: TRUE
# sims_output_path: either of
#   1. path of RDS file containing simulated output (EPRED, IPRED, EWRES, NPDE)
#   2. "" to use only NONMEM output from `bbr.bayes::nm_join_bayes_quick()`
  sims_output_path: ""
  # sims_output_path: !r here::here("model/pk/1000/diag-sims-1000.rds")
# n_post, resid_var, ipred_sim, and ci_level:
#   settings used in `nm_join_bayes()` (if applicable)
#   These are reflected only in text used to describe output
  n_post: 1000
  resid_var: TRUE
  ipred_sim: TRUE
  ci_level: 95
# plot_ci: if true, include CIs on DV vs prediction plots (only relevant when sims_output_path is not "")
  plot_ci: FALSE
  run_mrggsave: TRUE
---

# Run number `r params$run`

To produce a set of diagnostic plots that will be included in a report. Please
note that these plots are just meant to provide an example of what could be
created and how. They are not an exhaustive list of every possible plot and were
chosen with the project aims in mind.

# Set up

```{r setup_general, include = F}
### General script set-up
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.height = 5,
  fig.width = 5
)

### Libraries ----------------------------
suppressPackageStartupMessages(library(tidyverse))
library(pmplots)
library(bbr)
library(bbr.bayes)
suppressPackageStartupMessages(library(posterior))
library(bayesplot)
library(yspec)
library(mrggsave)
library(pmtables)
library(mrgsolve)
library(furrr)
library(patchwork)
library(glue)
library(cowplot)
library(here)

### Directories ----------------------------
figDir <- here::here("deliv", "figure", "report")
dataDir <- here::here("data")

if (!file.exists(figDir)) dir.create(figDir)

thisScript <- params$script
options(
  mrg.script = params$script,
  mrggsave.dev = "pdf,png"
)

theme_set(pmplots::pm_theme())

if (params$plot_ci && params$sims_output_path == "") {
  stop("Set `sims_output_path` (after running simulations) in order to plot CIs")
}
```


```{r load_any_functions, include = F}
### Source function scripts
source(here::here("script/functions-diagnostics.R"))
source(here::here("script/functions-diagnostics-rhat-ess.R"))
```

### Model location

Define `modelName` and path to the model directory (`MODEL_DIR`).

```{r setup_bbr, echo = params$include_code, message = FALSE}
# Set directories for bbr models ----------------------------
MODEL_DIR <- params$modelDir
modelName <- params$run
thisModelPath <- file.path(MODEL_DIR, modelName)
```

### Figure location

If saving figures out to pdf, define where those pdfs should be saved to.
Here the figures are saved to ```deliv > figure > model_run_number```

```{r makeDir_mrggsave, echo = params$include_code, eval = params$run_mrggsave}
thisFigDir <- file.path(figDir, modelName)
if (!file.exists(thisFigDir)) dir.create(thisFigDir)

### set mrggsave figure directory here
options(mrggsave.dir = thisFigDir)
```



# Model details

A summary of high-level model details.

Read in the model details using `read_model`. Details stored in the `mod` object
can be used to identify the location of the source data (used in $DATA) - to see
how this is done look at the `bbr::get_data_path()` and
`bbr::build_path_from_model()` helper functions.

```{r modelDetails, echo = params$include_code, results = "asis"}
mod <- read_model(file.path(MODEL_DIR, params$run))
mod
```

### Read output

```{r modelOutputSummary, echo = params$include_code}
# `draws_array` object from the `posterior` package
draws <- read_fit_model(mod)
n_chains <- nchains(draws)
n_iter <- niterations(draws)

# Summary of the posterior 
draws_param <- subset_draws(draws, variable = c("THETA", "OMEGA", "SIGMA"))
draws_sum <- draws_param %>% 
  summarize_draws()

# Calculate shrinkage from post hoc ETAs, or from the .shk files if the .iph
# files do not exist
shk0 <- shrinkage(mod)
omegas <- variables(draws) %>% 
  str_subset("^OMEGA") %>% 
  # diagonals only
  str_subset("\\[(\\d+),\\1\\]")
shk <- tibble(variable = omegas, shrinkage = shk0)
```

## Parameter estimates 

Compute summaries of posterior distributions as well as some diagnostics.

Bulk effective sample size (ESS) is a measure of sampling efficiency for the
location of the distribution, while Tail ESS is a measure of sampling efficiency
for the tails (5% and 95% quantiles) of the distribution. Higher values indicate
greater sampling efficiency.  A very rough rule of thumb is to aim for at least
400 for each parameter.

R-hat is a convergence diagnostic that compares the between- and within-chain
variances of model parameters. Values close to 1 indicate that the chains have
converged to similar distributions.  Aim for less than about 1.05 for all
parameters.

This is a repeat of the summary table produces in the MCMC diagnostics template,
but can be usedful to include here to refer to when considering model
diagnostics.

```{r summary, echo = FALSE}
ptable <- draws_sum %>% 
  mutate_if(is.numeric, ~formatC(., 3)) %>% 
  rename(parameter = variable) %>%
  mutate("90% CI" = paste("(", q5, ", ", q95, ")", 
                          sep = "")) %>%
  select(parameter, mean, median, sd, mad, "90% CI", ess_bulk, ess_tail, rhat)

ptable %>% 
  knitr::kable(caption = "Summary of model parameter estimates.")
```


# Read in data

Model output (EPRED, IPRED, NPDE, EWRES, ETAs) is read in from either the output
of simulations (see `?bbr.bayes::nm_join_bayes`) or from NONMEM output only.
When only NONMEM output is used, medians of these values across all chains are
calculated.

After reading in the NONMEM dataset and the output dataset they're joined by a
`NUM` column. **This assumes that a row number column (called `NUM`) was
included during data assembly.** The idea here is that in NONMEM, you table
just `NUM` and none of the other input data items. They all will get joined
back to the NONMEM output ... even character columns.

The `data` used in the diagnostic plots has been filtered to only include the
observations (i.e. `EVID==0`). Note that further modifications may be needed, for
example, if BLQ data was included in the model or if the `DV` was
log-transformed. The dataset also converts the categorical covariates of
interest to factors using the `yspec_add_factors` function and details described
in the spec file.

The `id` subset gets the first record per ID. This would usually be the baseline
value but consider filtering on a baseline flag if available. Also, if the model
includes inter-occasion variability (IOV), the occasion variable should be
included within the `distinct` function.

```{r read_in_data, echo = params$include_code, message=FALSE}
# load in the spec file
spec <- ys_load(params$yspec)

if (params$sims_output_path != "") {
  if (!file.exists(params$sims_output_path)) {
    stop(glue("File {params$sims_output_path} does not exist"))
  } else {
    data0 <- readRDS(params$sims_output_path)
  }
} else {
  data0 <- nm_join_bayes_quick(mod)
}

# filter to observation rows only
data <- data0 %>%
  filter(EVID == 0) %>%
  yspec_add_factors(spec, .suffix = "")

if (isTRUE(params$logDV)) {
  data <- mutate(data,
    LNPRED = PRED,
    PRED = exp(PRED),
  )
}

# filter to single row per ID and include factors
id <- distinct(data, ID, .keep_all = TRUE)
```

```{r desc_test, include = F}
# Descriptive text that depends on the settings used for diagnostic simulations
# (and whether diagnostic simulations were run at all)

ind_pred_text <- glue(
  "Individual predictions are medians of the values of IPRED output by NONMEM
  for each of the {n_chains} chains."
)
etas_text <- glue(
  "ETAs are medians of the values
  of ETA output by NONMEM for each of the {n_chains} chains."
)
if (params$sims_output_path == "") {
  # Medians of NONMEM output only
  pop_pred_text <- glue(
    "Population predictions are medians of the values of EPRED output by NONMEM
    for each of the {n_chains} chains."
  )
  dv_pred_text <- glue(pop_pred_text, ind_pred_text, .sep = " ")
  npde_text <- glue(
    "Normalized prediction distribution errors (NPDE) are medians of the values
    of NPDE output by NONMEM for each of the {n_chains} chains."
  )
  ewres_text <- glue(
    "Expected weighted residuals (EWRES) are medians of the values
    of EWRES output by NONMEM for each of the {n_chains} chains."
  )
} else {
  # Medians (and optionally upper/lower percentiles) from simulations
  pop_pred_text <- glue(
    "Population predictions are medians of {params$n_post} simulated values
    incorporating between-{ifelse(params$resid_var, ' and within-', '')}subject
    variability, as well as uncertainty in population parameter estimates via
    sampling from the posterior distribution."
  )
  if (params$ipred_sim) {
    ind_pred_text <- glue(
      "Individual predictions are medians of {params$n_post} simulated values
      incorporating conditional estimates of individual parameters and include
      {ifelse(params$resid_var, 'within-subject variability, as well as', '')}
      uncertainty in population parameter estimates via sampling from the
      posterior distribution."
    )
    etas_text <- glue(
      "ETAs are medians of {params$n_post} posterior ETAs across
      the {n_chains} chains."
    )
  }
  dv_pred_text <- glue(pop_pred_text, ind_pred_text, .sep = " ")
  if (params$plot_ci) {
    dv_pred_text <- glue(
      dv_pred_text,
      " Red error bars represent {params$ci_level}% CIs."
    )
  }
  npde_text <- glue(
    "Normalized prediction distribution errors (NPDE) are Monte-Carlo generated
    diagnostics, using {params$n_post} simulations incorporating
    between-{ifelse(params$resid_var, ' and within-', '')}subject variability,
    as well as uncertainty in population parameter estimates via
    sampling from the posterior distribution."
  )
  ewres_text <- glue(
    "Expected weighted residuals (EWRES) are Monte-Carlo generated residuals,
    using {params$n_post} simulations incorporating
    between-{ifelse(params$resid_var, ' and within-', '')}subject variability,
    as well as uncertainty in population parameter estimates via
    sampling from the posterior distribution."
  )
}
```



# General diagnostic plots

The following plots assume that the preferred x-axis labels are defined here. 

```{r xAxis_label_names, echo = params$include_code}
### Ideally get units from yaml

xTIME <- "TIME //Time (h)"
xTAD <- "TAD //Time after dose (h)"
xPRED <- "EPRED //Population predicted concentration"
yEWRES <- "EWRES //Expected weighted residual"
yNPDE <- "NPDE //Normalized prediction distribution error"
```

## DV vs population and individual predictions

Create plots of DV vs population and individual predictions for the full dataset
and stratified by renal function and hepatic function.

```{r DV_PRED_plots, echo = params$include_code, message=FALSE}
# DV vs population predictions
dv_pred_ci <- function(data, scales_free = FALSE) {
  p <- ggplot(data = data, aes(x = EPRED, y = DV)) + 
    geom_errorbarh(aes(xmin = EPRED_lo, xmax = EPRED_hi), 
                   colour = "red3", alpha = 0.3) + 
    geom_point() + 
    xlab(glue("Population predicted value")) + ylab("Observed value") +  
    pm_abline() + pm_smooth() + pm_theme()
  if (!scales_free) {
    p <- p +
      lims(
        x = c(0, max(data$EPRED_hi)),
        y = c(0, max(data$EPRED_hi))
      )
  }
  p
}
if (params$plot_ci & params$sims_output_path != "") {
  dvp <- dv_pred_ci(data)
  # by renal function
  dvp_rf <- dv_pred_ci(data, scales_free = TRUE) +
    facet_wrap(~RF, scales = "free")
  # by hepatic function
  dvp_cp <- dv_pred_ci(data, scales_free = TRUE) +
    facet_wrap(~CP, scales = "free")
} else {
  dvp <- dv_pred(data, x = "EPRED//Population predicted {xname}")
  # by renal function
  dvp_rf <- dv_pred(data, x = "EPRED//Population predicted {xname}", scales = "free") +
    facet_wrap(~RF, scales = "free")
  # by hepatic function
  dvp_cp <- dv_pred(data, x = "EPRED//Population predicted {xname}", scales = "free") +
    facet_wrap(~CP, scales = "free")
}

# DV vs individual predictions
dv_ipred_ci <- function(data, scales_free = FALSE) {
  p <- ggplot(data = data, aes(x = IPRED, y = DV)) + 
    geom_errorbarh(aes(xmin = IPRED_lo, xmax = IPRED_hi), 
                   colour = "red3", alpha = 0.3) + 
    geom_point() + 
    xlab("Individual predicted value") + ylab("Observed value") +  
    pm_abline() + pm_smooth() + pm_theme()
  if (!scales_free) {
    p <- p +
      lims(
        x = c(0, max(data$IPRED_hi)),
        y = c(0, max(data$IPRED_hi))
      )
  }
  p
}
if (params$plot_ci & params$sims_output_path != "" &
    "IPRED_lo" %in% names(data)) {
  dvip <- dv_ipred_ci(data)
  # by renal function
  dvip_rf <- dv_ipred_ci(data, scales_free = TRUE) +
    facet_wrap(~RF, scales = "free")
  # by hepatic function
  dvip_cp <- dv_ipred_ci(data, scales_free = TRUE) +
    facet_wrap(~CP, scales = "free")
} else {
  dvip <- dv_ipred(data, x = "IPRED//Individual predicted {xname}")
  # by renal function
  dvip_rf <- dv_ipred(data, x = "IPRED//Individual predicted {xname}", scales = "free") +
    facet_wrap(~RF, scales = "free")
  # by hepatic function
  dvip_cp <- dv_ipred(data, x = "IPRED//Individual predicted {xname}", scales = "free") +
    facet_wrap(~CP, scales = "free")
}

p <- pm_grid(list(dvp, dvip), nrow = 2, ncol = 1)
```

```{r results="asis", include=params$include_plots, echo=F}
dv_pred_text
```

```{r include_DV_PRED, include=params$include_plots, echo=F, message=FALSE}
p
```

DV vs population and individual predictions by renal function

```{r include_DV_PRED_rf, include=params$include_plots, echo=F, message=FALSE}
dvp_rf ; dvip_rf
```

DV vs population and individual predictions by hepatic function

```{r include_DV_PRED_cp, include=params$include_plots, echo=F, message=FALSE}
dvp_cp ; dvip_cp
```


```{r save_DV_PRED, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  stem = c(params$run, "dv-pred-ipred"),
  width = 5,
  height = 7
)


mrggsave(
  list(dvp_rf, dvip_rf), 
  stem = c(params$run, "dv-pred-ipred-byRF"),
  width = 5,
  height = 5
)
mrggsave(
  list(dvp_cp, dvip_cp), 
  stem = c(params$run, "dv-pred-ipred-byCP"),
  width = 5,
  height = 5
)
```

```{r rm_dv_pred, include=F}
rm(p, dvp, dvip, dvp_rf, dvip_rf, dvp_cp, dvip_cp)
```


## NPDE plots

```{r results="asis", include=params$include_plots, echo=F}
npde_text
```

NPDE vs population predictions, time and time after dose.

```{r results="asis", include=params$include_plots, echo=F}
pop_pred_text
```

```{r NPDE_plots, echo = params$include_code, message = FALSE}
## Plan to display these three plots in a single, 3 panel figure and so the y-axis
## labels are removed manually for display purposes
p1 <- npde_pred(data, x = xPRED, y = "NPDE //  ")
p2 <- npde_time(data, x = xTIME)
p3 <- npde_tad(data, x = xTAD, y = "NPDE //  ")

p <- pm_grid(list(p1, p2, p3), nrow = 3, ncol = 1)
```

```{r include_NPDE, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE, fig.height = 7}
p
```

```{r save_NPDE, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-pred-time-tad"),
  width = 5,
  height = 7
)
```

```{r rm2, include = F}
rm(p)
```


NPDE vs continuous covariates

```{r NPDE_cont_cov_plots, echo = params$include_code, message = FALSE}
NPDEco <- spec %>%
  ys_select(params$contCov) %>% # select the covariates of interest
  axis_col_labs(
    title_case = TRUE, # converts yspec short to title_case
    short_max = 20
  ) # if yspec short is >10 characters it keeps the abbreviation

p1 <- npde_cont(data, x = NPDEco[1])
p2 <- npde_cont(data, x = NPDEco[2])
p3 <- npde_cont(data, x = NPDEco[3])
p4 <- npde_cont(data, x = NPDEco[4])

p <- pm_grid(list(p1, p2, p3, p4), ncol = 1)
```

```{r include_NPDE_cont_cov, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE, fig.height = 7}
p
```

```{r save_NPDE_cont_cov, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-cont-cov"),
  width = 5,
  height = 7
)
```

```{r rm2_cont_cov, include = F}
rm(p)
```

NPDE vs categorical covariates.

```{r NPDE_cat_cov_plots, echo = params$include_code, message = FALSE}
NPDEca <- spec %>%
  ys_select("RF", "CP") %>%   # select the covariates of interest
  axis_col_labs(title_case = TRUE) # converts yspec short to title_case

p1 <- npde_cat(data, x = NPDEca[1])
p2 <- npde_cat(data, x = NPDEca[2]) + rot_x(45)

p <- pm_grid(list(p1, p2), nrow = 2, ncol = 1)
```

```{r include_NPDE_cat_cov, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_NPDE_cat_cov, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-cat-cov"),
  width = 5,
  height = 7
)
```

```{r rm2_cat_cov, include = F}
rm(p)
```


## NPDE density histogram

```{r npde_hist_plots, echo = params$include_code, message = FALSE}
p <- npde_hist(data)
```

```{r include_npde_hist, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_npde_hist, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "npde-hist"),
  width = 5,
  height = 5
)
```

```{r rm3, include = F}
rm(p)
```

## EWRES vs population predictions, time and time after dose

```{r results="asis", include=params$include_plots, echo=F}
ewres_text
```

```{r results="asis", include=params$include_plots, echo=F}
pop_pred_text
```

```{r ewres_plots, echo = params$include_code, message=FALSE}
p_ewres_epred <- res_pred(data, x = xPRED, y = yEWRES)
p_ewres_time <- res_pred(data, x = xTIME, y = yEWRES)
p_ewres_tad <- res_pred(data, x = xTAD, y = yEWRES)
p <- pm_grid(
  list(
    p_ewres_epred,
    p_ewres_time,
    p_ewres_tad
  ),
  nrow = 3,
  ncol = 1
)
```

```{r include_ewres, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE, fig.height = 7}
p
```

```{r save_ewres, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  stem = c(params$run, "ewres-epred-time-tad"),
  width = 5,
  height = 7
)
```

```{r rm_ewres_plots, include=F}
rm(p)
```



## EWRES qq and density plot

```{r ewres_qq_density_plots, echo = params$include_code, message=FALSE}
p_ewres_q <- wres_q(data, "EWRES")
p_ewres_hist <- cont_hist(data, "EWRES", y = "..density..")
p <- pm_grid(list(p_ewres_q, p_ewres_hist), nrow = 2, ncol = 1)
```

```{r include_ewres_qq_density, eval=params$include_plots, include=params$include_plots, echo=F, message=FALSE}
p
```

```{r save_ewres_qq_density, include = FALSE, eval = params$run_mrggsave, message=FALSE}
mrggsave(
  p,
  stem = c(params$run, "ewres-qq-hist"),
  width = 5,
  height = 7
)
```

```{r rm_ewres_qq_density, include=F}
rm(p)
```



# EBEs-based diagnostics

```{r results="asis", include=params$include_plots, echo=F}
etas_text
```



## ETA pairs plot 

```{r eta_pairs_plots, echo = params$include_code, message = FALSE}
p <- eta_pairs(id, params$etas)
```

```{r include_eta_pairs, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_eta_pairs, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "eta", "pairs"),
  width = 5,
  height = 5
)
```

```{r rm5, include = F}
rm(p)
```





## Continuous covariate plots

These plots uses yspec to automatically rename the axis labels.

```{r get_cont_cov_labels, echo = params$include_code}
co <- spec %>%
  ys_select(params$contCov) %>% # select the covariates of interest
  axis_col_labs(
    title_case = TRUE, # converts yspec short to title_case
    short_max = 20
  ) # if yspec short is >10 characters it keeps the abbreviation
```

### ETA vs continuous covariates

Note that here we use a function that maps over the ETAs (not the covariates)
because the purpose of these plots was to determine whether there were any
trends in the covariates for a given ETA. This may need to be edited to address
different study specific questions

```{r eta_vs_cont_plots, echo = params$include_code, message = FALSE}
p <- purrr::map(.x = params$etas, ~ map_wrap_eta_cont(.x, co, id, .ncol = 1))
```

```{r include_eta_vs_cont, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_eta_vs_cont, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "eta-all", "cont", "cov"),
  width = 5,
  height = 5
)
```

```{r rm6, include = F}
rm(p)
```

### Continuous covariate pairs plot

```{r contCov_pairs_plots, echo = params$include_code, message = FALSE}
co2 <- str_replace(co, "\\(", "\n(")
p <- eta_pairs(id, co2) + rot_x(45)
```

```{r include_contCov_pairs, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_contCov_pairs, include = FALSE, eval = params$run_mrggsave, message = FALSE}
mrggsave(
  p,
  stem = c(params$run, "eta", "all", "contCov", "pairs"),
  width = 5,
  height = 6
)
```

```{r rm7, include = F}
rm(p)
```


## Categorical covariate plots

These plots uses the yspec to automatically rename the axis labels.

```{r get_cat_cov_labels, echo = params$include_code}
ca <- spec %>%
  ys_select(params$catCov) %>% # select the covariates of interest
  axis_col_labs(title_case = TRUE) # converts yspec short to title_case
```


### ETA vs categorical covariates

Note that here we use a function that maps over the covariates (not the ETAs)
because the purpose of these plots was to determine whether there is any
difference in the distribution of ETAs across studies, dosing groups and disease
states. This should be updated to reflect the questions you're trying to
address.


```{r eta_vs_cat_plots, echo = params$include_code, message = FALSE}
if (length(params$etas) > 1) {
  p <- purrr::map(.x = ca, ~ map_eta_cat(.x, params$etas, id))
} else {
  ## CHECK: depending on the labels, this may need to be changed
  p <- purrr::map(.x = ca, ~ eta_cat(id, .x, params$etas) + rot_x(35))
}

pList <- pm_grid(list(p[[1]], p[[2]]), nrow = 2, ncol = 1)
```

```{r include_eta_vs_cat, eval = params$include_plots, include = params$include_plots, echo = F, message = FALSE}
p
```

```{r save_eta_vs_cat, include = FALSE, eval = params$run_mrggsave, message = FALSE}
## As of mrggsave v0.4.0, if you pass mrggsave a named list of plots, it will use this to
## name the plots that it writes out (regardless of whether stem is defined).
## If you don't want to use this feature, you can pass unname(p), instead of just p
mrggsave(
  list(pList, unname(p)),
  stem = c(params$run, "eta", "all", "cat", "cov"),
  width = 5,
  height = 7
)
```


# Session details

It is considered good practice to include these details at the end of all rmd scripts

```{r details, include = TRUE}
Sys.getenv("AMI_NAME")
sessioninfo::session_info()
bbr::bbi_version()
```
